\sysfull

### 2017-08-09 paper/evaluation.tex
added environment

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version X~\cite{}\todo{Report on CCS version; CMUs environment}{Kiwan/Amjad}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.

>>>>

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version X~\cite{}\todo{Report on CCS version}{Amjad}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.

We also had alternative setup where we used MSP-TS430RGZ48C launchpad for continuous power experiment. We used internal timer for measuring run time. For harvested energy, we used ThingMagic Astra-EX RFID reader with power level of 17.25-30dBm. We used EDB~\cite{edb} for run time measurement. Applications were cross compiled using GCC and Clang, so that we can use LLVM for \sys compiler.
